NOSQL\\ BEST PRACTICES

### 2018-04-03 pgconfus2018/presentation.tex
Mention JIT compilation for tuple deform
Remove duplicated slide
Add slide about sql null vs jsonb null
Add step-by-step version for wal diff schema

        \begin{itemize}[label={\MVRightarrow}]
            \item Keep at the end for readability
            \item tuple\_deform
        \end{itemize}

@@

@@

    \vspace{1cm}
    \begin{tikzpicture}
        \draw[line width=0.5mm] (0,0) rectangle (2,1) node[pos=.5] {};
        \draw[line width=0.5mm] (2,0) rectangle (4,1) node[pos=.5] {};
        \draw[line width=0.5mm] (4,0) rectangle (6,1) node[pos=.5] {};
        \draw[line width=0.5mm, fill=red!30] (6,0) rectangle (8,1) node[pos=.5] {DIFF};
        \draw[line width=0.5mm] (8,0) rectangle (10,1) node[pos=.5] {};
        \draw[line width=0.5mm] (10,0) rectangle (12,1) node[pos=.5] {};
        \draw[->, line width=1mm, dashed] (0,-0.5) -- (6,-0.5);
        \draw[<-, line width=1mm, dashed] (8,-0.5) -- (12,-0.5);
    \end{tikzpicture}

    \begin{tikzpicture}
        \draw[line width=0.5mm] (0,0) rectangle (2,1) node[pos=.5] {\{};
        \draw[line width=0.5mm, fill=red!30] (2,0) rectangle (4,1) node[pos=.5] {DIFF};
        \draw[line width=0.5mm, fill=red!30] (4,0) rectangle (6,1) node[pos=.5] {};
        \draw[line width=0.5mm, fill=red!30] (6,0) rectangle (8,1) node[pos=.5] {};
        \draw[line width=0.5mm, fill=red!30] (8,0) rectangle (10,1) node[pos=.5] {DIFF};
        \draw[line width=0.5mm] (10,0) rectangle (12,1) node[pos=.5] {\}};
        \draw[->, line width=1mm, dashed] (0,-0.5) -- (2,-0.5);
        \draw[<-, line width=1mm, dashed] (10,-0.5) -- (12,-0.5);
    \end{tikzpicture}

>>>>

        \begin{itemize}[label={\MVRightarrow}]
            \item Keep at the end for readability
            \item tuple\_deform (PG11, JIT compilation)
        \end{itemize}

@@

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Jsonb NULL != SQL NULL}

        \inputminted[
            fontsize=\Large,
            escapeinside=||
        ]{sql}{sql/jsonb_sql_null.sql}

        \inputminted[
            fontsize=\large,
        ]{bash}{sql/jsonb_sql_null.sh}

        \inputminted[
            fontsize=\Large,
            escapeinside=||
        ]{sql}{sql/jsonb_null.sql}

        \inputminted[
            fontsize=\large,
        ]{bash}{sql/jsonb_null.sh}

@@

    \vspace{0.5cm}
    \onslide<1,2,3,4,5>
    \begin{tikzpicture}
        \draw[line width=0.5mm] (0,0) rectangle (2,1) node[pos=.5] {};
        \draw[line width=0.5mm] (2,0) rectangle (4,1) node[pos=.5] {};
        \draw[line width=0.5mm] (4,0) rectangle (6,1) node[pos=.5] {};
        \draw[line width=0.5mm, fill=red!30] (6,0) rectangle (8,1) node[pos=.5] {DIFF};
        \draw[line width=0.5mm] (8,0) rectangle (10,1) node[pos=.5] {};
        \draw[line width=0.5mm] (10,0) rectangle (12,1) node[pos=.5] {};
    \end{tikzpicture}

    \vspace{-0.5cm}
    \onslide<2,3,4,5>
    \begin{tikzpicture}
        \draw[->, line width=1mm, dashed] (0,-0.5) -- (6,-0.5);
        \draw[<-, line width=1mm, dashed] (8,-0.5) -- (12,-0.5);
    \end{tikzpicture}

    \vspace{0.5cm}
    \onslide<3>
    \begin{tikzpicture}
        \draw[line width=0.5mm] (0,0) rectangle (2,1) node[pos=.5] {\{};
        \draw[line width=0.5mm, fill=red!30] (2,0) rectangle (4,1) node[pos=.5] {DIFF};
        \draw[line width=0.5mm] (4,0) rectangle (6,1) node[pos=.5] {};
        \draw[line width=0.5mm] (6,0) rectangle (8,1) node[pos=.5] {};
        \draw[line width=0.5mm, fill=red!30] (8,0) rectangle (10,1) node[pos=.5] {DIFF};
        \draw[line width=0.5mm] (10,0) rectangle (12,1) node[pos=.5] {\}};
    \end{tikzpicture}

    \vspace{-1.28cm}
    \onslide<4>
    \begin{tikzpicture}
        \draw[line width=0.5mm] (0,0) rectangle (2,1) node[pos=.5] {\{};
        \draw[line width=0.5mm, fill=red!30] (2,0) rectangle (4,1) node[pos=.5] {DIFF};
        \draw[line width=0.5mm] (4,0) rectangle (6,1) node[pos=.5] {};
        \draw[line width=0.5mm] (6,0) rectangle (8,1) node[pos=.5] {};
        \draw[line width=0.5mm, fill=red!30] (8,0) rectangle (10,1) node[pos=.5] {DIFF};
        \draw[line width=0.5mm] (10,0) rectangle (12,1) node[pos=.5] {\}};
        \draw[->, line width=1mm, dashed] (0,-0.5) -- (2,-0.5);
        \draw[<-, line width=1mm, dashed] (10,-0.5) -- (12,-0.5);
    \end{tikzpicture}

    \vspace{-1.8cm}
    \onslide<5>
    \begin{tikzpicture}
        \draw[line width=0.5mm] (0,0) rectangle (2,1) node[pos=.5] {\{};
        \draw[line width=0.5mm, fill=red!30] (2,0) rectangle (4,1) node[pos=.5] {DIFF};
        \draw[line width=0.5mm, fill=red!30] (4,0) rectangle (6,1) node[pos=.5] {};
        \draw[line width=0.5mm, fill=red!30] (6,0) rectangle (8,1) node[pos=.5] {};
        \draw[line width=0.5mm, fill=red!30] (8,0) rectangle (10,1) node[pos=.5] {DIFF};
        \draw[line width=0.5mm] (10,0) rectangle (12,1) node[pos=.5] {\}};
        \draw[->, line width=1mm, dashed] (0,-0.5) -- (2,-0.5);
        \draw[<-, line width=1mm, dashed] (10,-0.5) -- (12,-0.5);
    \end{tikzpicture}
